\plaintitle

### 2016-05-21 Paper/sp2-paper.tex
Add abstract

% \begin{abstract}
% \end{abstract}
% 
% \category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
% 
\keywords{student; information; registration; enrollment}

@@

\section{Timeline}
\begin{center}
    \begin{tabular}[!htbp]{ | l | p{5cm} |}
    \hline
      Date & Activity \\ \hline
      Day 0-7 & Planning of System Framework and Database Structures \\ \hline
      Day 8-14 & Implementation of Basic Backend Functions Without Conflict Checking \\ \hline
      Day 15-30 & Implementation of Conflict Checking and Integration with Backend \\ \hline
      Day 31-45 & Development of Static Web Application Interface \\ \hline
      Day 46-60 & Implementation of Advanced Features \\ \hline
      Day 61-68 & Stress Testing and Fuzzing \\ \hline
      Day 69-76 & Adjustments from the Results of Stress Testing and Fuzzing \\ \hline
      Day 77-81 & Alpha Test of Test Users \\ \hline
      Day 82-96 & Adjustments from the Results of Alpha Test \\ \hline
      Day 97-103 & Beta Release \\ \hline
    \end{tabular}
\end{center}

\section{Results and Discussion}
\begin{tikzpicture}
  \begin{axis}[ ybar, 
		legend style={at={(0.5,-0.2)}, 
		anchor=north,legend columns=-1}, 
		ylabel={1000x Req/s}, 
		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
		xtick=data, 
		nodes near coords, 
		nodes near coords align={vertical}, 
		x tick label style={rotate=45,anchor=east}, ]
		\addplot coordinates {(Enlist,65.5) (Cancel,49.0) (Get Sched,140.9) (Get Slots,102.3) (Waitlist,69.0) (Unwaitlist,73.7)};
  \end{axis}
\end{tikzpicture}
\begin{center}
  Figure 1. Database requests per second
\end{center}
\begin{tikzpicture}
  \begin{axis}[ ybar, 
		legend style={at={(0.5,-0.2)}, 
		anchor=north,legend columns=-1}, 
		ylabel={1000x Req/s}, 
		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
		xtick=data, 
		nodes near coords, 
		nodes near coords align={vertical}, 
		x tick label style={rotate=45,anchor=east}, ]
		\addplot coordinates {(Enlist,18.1) (Cancel,17.7) (Get Sched,17.1) (Get Slots,17.6) (Waitlist,17.5) (Unwaitlist,17.7)};
  \end{axis}
\end{tikzpicture}
\begin{center}
  Figure 2. API server requests per second on a Dual Core i7-5600U
\end{center}

>>>>

\begin{abstract}
One of the challenges of universities with high student populations in the Philippines is the implementation of
an online enrollment system. Many of these systems were not tested to handle sudden heavy influx of user connections
and the technologies used are not best-fitted for such occurence. In this research, we design and implement a system
that can perform well under sudden surge of users by applying recent technological advances and design techniques. 
We use Redis as the database for fast atomic database access, Rust as a language with Iron as the web server framework for faster 
serving of HTTP requests by removing the need for a garbage collector, and the split client-server architecture that allows
the offloading of heavy content to static servers. The implemented system is tested by running benchmarks on both the database and
the server that will handle HTTP requests and measuring the number of requests per second. From this, we can see how it will perform
during sudden heavy load that occur during the online registration period. The results proved the efficiency of the system by showing
that it can serve an average of 17,600 requests per second with the database serving 83,400 requests per second on a dual-core system.
Moreover, because the system is designed to be multithreaded and utilize all cores, the server should be able to linearly scale when
more cores are added making it able to serve more than 50,000 requests on a higher-end computer. In the future, improvements in the Iron
web server framework such as asynchronous IO, and faster parsing algorithms could further improve the server speed of the system
as they are some of the bottlenecks of the system.
\end{abstract}
% 
% \category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
% 
\keywords{student; information; registration; enrollment; Rust; Redis; static webapp}

@@

\section{Results and Discussion}
\begin{tikzpicture}
  \begin{axis}[ ybar, 
		legend style={at={(0.5,-0.2)}, 
		anchor=north,legend columns=-1}, 
		ylabel={1000x Req/s}, 
		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
		xtick=data, 
		nodes near coords, 
		nodes near coords align={vertical}, 
		x tick label style={rotate=45,anchor=east}, ]
		\addplot coordinates {(Enlist,65.5) (Cancel,49.0) (Get Sched,140.9) (Get Slots,102.3) (Waitlist,69.0) (Unwaitlist,73.7)};
  \end{axis}
\end{tikzpicture}
\begin{center}
  Figure 1. Database requests per second on a Dual Core i7-5600U
\end{center}
\begin{tikzpicture}
  \begin{axis}[ ybar, 
		legend style={at={(0.5,-0.2)}, 
		anchor=north,legend columns=-1}, 
		ylabel={1000x Req/s}, 
		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
		xtick=data, 
		nodes near coords, 
		nodes near coords align={vertical}, 
		x tick label style={rotate=45,anchor=east}, ]
		\addplot coordinates {(Enlist,18.1) (Cancel,17.7) (Get Sched,17.1) (Get Slots,17.6) (Waitlist,17.5) (Unwaitlist,17.7)};
  \end{axis}
\end{tikzpicture}
\begin{center}
  Figure 2. API server requests per second on a Dual Core i7-5600U
\end{center}
